Approximation as Differentiation: Notes

### 2025-05-16 notes/cmon-enriched.tex
Show why CMon-enriched Yoneda embedding preserves biproducts.

The $\CMon$-enriched Yoneda embedding preserves biproducts:

\begin{proposition}
\end{proposition}

>>>>

The $\CMon$-enriched Yoneda embedding preserves biproducts, where (as in any functor category) biproducts in
$\PSh_{\CMon}(\cat{C})$ are computed pointwise.

\begin{proposition}
$\Yoneda_{\CMon}(X \biprod Y) \iso \Yoneda_{\CMon}(X) \biprod \Yoneda_{\CMon}(Y)$.
\end{proposition}

\begin{proof}
Suppose $Z$ an object in $C$. Then $\Yoneda_{\CMon}(X \biprod Y)(Z) = \Hom{\cat{C}}{Z}{X \biprod Y}$. But for
any $f: Z \to X \biprod Y$ in $\cat{C}$, there exist unique morphisms $f_1: Z \to X$ and $f_2: Z \to Y$ such
that $f = \biinj_X \comp f_1 + \biinj_Y \comp f_2$ by the universal property of the biproduct. Thus we have
$\Hom{\cat{C}}{Z}{X \biprod Y} \iso \Hom{\cat{C}}{Z}{X} \biprod \Hom{\cat{C}}{Z}{Y} = \Yoneda_{\CMon}(X)(Z)
\biprod \Yoneda_{\CMon}(Y)(Z) = (\Yoneda_{\CMon}(X) \biprod \Yoneda_{\CMon}(Y))(Z)$.
\end{proof}
